Titeln på avhandlingens språk

### 2022-11-04 implications_optimization.tex
update plots

\begin{figure*}
    \centering
    \begin{subtable}[t]{.3\textwidth}
        \centering
        \caption{Parameters used for \textcite{Wang2019Towards}'s adaptive sampling scheme.}
        \medskip
        \begin{tabular}{lr}
            \toprule
            \( R_\text{min} \)  & \SI{0.5}{\hertz} \\
            \( \alpha \)        & \num{3.0} \\
            \ac{RTT}            & \SIlist{150;300;600}{\milli\second} \\
            \bottomrule
        \end{tabular}
    \end{subtable}%
    \hspace{.05\textwidth}%
    % \begin{subfigure}[]{\columnwidth}
    %     \centering
    %     \includegraphics[width=\textwidth]{figs/new_model/sampling_junjue.png}
    %     \caption{%
    %         Mean number of samples per step over a \num{100}-step task, \num{90} independent repetitions per configuration.
    %         Error bars indicate \SI{95}{\percent} \acp{CI}.
    %     }
    % \end{subfigure}
    \begin{subtable}[t]{.6\textwidth}
        \centering
        \caption{Mean number of captured samples per sampling scheme at the three different \acp{RTT}.}
        \medskip
        \begin{tabular}{lrrr}
            \toprule
            Sampling scheme & \SI{150}{\milli\second} & \SI{300}{\milli\second} & \SI{600}{\milli\second} \\
            \midrule
            Adaptive (ED2 LN) & \num{14.69} & \num{8.07} & \num{5.10} \\
            Adaptive (ED2 HN) & \num{14.60} & \num{8.03} & \num{5.05} \\
            Adaptive (ED2 LN, ExG fit) & \num{15.30} & \num{8.23} & \num{5.09} \\
            Adaptive (ED2 HN, ExG fit) & \num{15.05} & \num{8.47} & \num{5.20} \\
            Adaptive (reference, gaussian fit) & \num{20.17} & \num{10.65} & \num{6.04} \\
            Greedy & \num{36.68} & \num{19.11} & \num{10.36} \\
            \bottomrule
        \end{tabular}
    \end{subtable}\\
    \bigskip
    \begin{subfigure}[]{\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{figs/new_model/diff_sampling_junjue.png}
        \caption{%
            Percentage reduction in mean number of captured samples per step (higher is better).
            Error bars indicate the \SI{95}{\percent} \acp{CI}, calculated using a two-sided T-test.
            % \todo[inline]{%
            %     Add greedy.
            %     Develop optimal sampling scheme?
            %     Explain grouping better?
            % }
        }
    \end{subfigure}
    \caption{%
        Results of parameterizing \textcite{Wang2019Towards}'s adaptive sampling scheme using the realistic timing model.
        \emph{ED2} indicates a sampling scheme using the \edgedroid{} model for \ac{CDF} estimation.
        \emph{HN} and \emph{LN} indicate high or low neuroticism, respectively, and \emph{ExG fit} indicates a timing model which fits an \ac{exGaussian} distribution to the execution time data for each step.
    }\label{fig:samples}
\end{figure*}

The results of this investigation are presented in \cref{fig:samples}
They clearly show the potentially dramatic effects of more accurate execution time estimation when optimizing sampling rates.
When using the realistic model for execution time estimation, the sampling schemes achieve between \SI{14}{\percent} and \textasciitilde\SI{27}{\percent} better average performance, depending on the \edgedroid{} model parameterization and the system \ac{RTT}.
\todo[inline]{Discuss that lower RTTs lead to better results?}
This is true even for configurations with low neuroticism which do not exactly match the parameterization of the external timing model driving the execution times for the steps, showing thus the importance of even less-accurate approximations.

@@

@@

    Plot energy consumption over RTT, mean energy per step over a task.
    Ground truth empirical high.
    For greedy, ideal, junjues sampling, vishnus model with gt as estimator.
}

>>>>

\begin{figure*}
    \centering
    \begin{subtable}[t]{.25\textwidth}
        \centering
        \caption{Parameters used for \textcite{Wang2019Towards}'s adaptive sampling scheme.}
        \medskip
        \begin{tabular}{lr}
            \toprule
            \( R_\text{min} \)  & \SI{0.5}{\hertz} \\
            \( \alpha \)        & \num{3.0} \\
            \ac{RTT}            & \SIlist{150;300;600}{\milli\second} \\
            \bottomrule
        \end{tabular}
    \end{subtable}%
    \hspace{.05\textwidth}%
    \begin{subtable}[t]{.65\textwidth}
        \centering
        \caption{Mean number of captured samples per sampling scheme at the three different \acp{RTT}.}
        \medskip
        \begin{tabular}{llrrr}
            \toprule 
            Timing model neuro. & Sampling scheme & \SI{150}{\milli\second} & \SI{300}{\milli\second} & \SI{600}{\milli\second} \\
           \midrule
           \multirow[c]{2}{*}{Low} & Greedy & \num{36.53} & \num{18.88} & \num{10.52} \\
            & Adaptive Gaussian fit & \num{19.97} & \num{10.43} & \num{6.39} \\
           \multirow[c]{2}{*}{High} & Greedy & \num{37.05} & \num{19.04} & \num{10.89} \\
            & Adaptive Gaussian fit & \num{20.29} & \num{10.79} & \num{6.67} \\
            \bottomrule
        \end{tabular}
    \end{subtable}\\
    \bigskip
    \begin{subfigure}[]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/diff_sampling_junjue_both.png}
        \caption{%
            Percentage reduction in mean number of captured samples per step (higher is better).
            Error bars indicate the \SI{95}{\percent} \acp{CI}, calculated using a two-sided T-test.
            \todo[inline]{%
                % Vishnu: minimize number of samples.
                I don't like the two plots, I think the message gets diluted and confusing.
                I suggest only keeping one ``ground truth'', high neuroticism.
                Otherwise, every plot and table needs to be duplicated.
            }
        }
    \end{subfigure}
    \caption{%
        Results of parameterizing \textcite{Wang2019Towards}'s adaptive sampling scheme using the realistic timing model.
        \emph{ED2} indicates a sampling scheme using the \edgedroid{} model for \ac{CDF} estimation.
        \emph{HN} and \emph{LN} indicate high or low neuroticism, respectively, and \emph{ExG fit} indicates a timing model which fits an \ac{exGaussian} distribution to the execution time data for each step.
    }\label{fig:samples}
\end{figure*}

The results of this investigation are presented in \cref{fig:samples}
They clearly show the potentially dramatic effects of more accurate execution time estimation when optimizing sampling rates.
When using the realistic model for execution time estimation, the sampling schemes achieve between \SI{14}{\percent} and \textasciitilde\SI{27}{\percent} better average performance, depending on the \edgedroid{} model parameterization and the system \ac{RTT}.
\todo[inline]{Update with new ground truths.}
This is true even for configurations with low neuroticism which do not exactly match the parameterization of the external timing model driving the execution times for the steps, showing thus the importance of even less-accurate approximations.

@@

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{figs/new_model/sampling_energy.png}
        \caption{}
    \end{subfigure}\\
    \medskip
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{figs/new_model/sampling_energy_diff.png}
        \caption{}
    \end{subfigure}
\end{figure*}

@@

    Explain plots.
}
